Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-21 paper.qmd
Render the projection after scaling as a valdation

axis_scale <- 2 * limits/3
axis_pos <- -0.6 * limits

@@

axis_scale <- 0.15 * limits
axis_pos <- -0.6 * limits
adj <- function(x) axis_pos + x * axis_scale
theta <- seq(0, 2 * pi, length = 50)
circle <- data.frame(c1 = adj(cos(theta)), c2 = adj(sin(theta)))

@@

axis_scale <- 2 * limits/3
axis_pos <- -0.4 * limits

@@

axis_scale <- 0.1 * limits
axis_pos <- -0.4 * limits
adj <- function(x) axis_pos + x * axis_scale
theta <- seq(0, 2 * pi, length = 50)
circle <- data.frame(c1 = adj(cos(theta)), c2 = adj(sin(theta)))

@@

```{r}
#| label: fig-scurve-true-sc
#| fig-cap: "Two views of the true model (blue lines) in $2\\text{-}D$ projections from $7\\text{-}D$, for the S-curve data (black points). The data is spread along the S shape, and does not vary much from this curve. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/I5GL23vLiw0>)." 
#| fig-width: 10
#| fig-height: 7
#| fig-pos: H

>>>>

# axis_scale <- 2 * limits/3
# axis_pos <- -0.6 * limits
axis_scale <- limits/6
axis_pos <- -2/3 * limits

@@

# axis_scale <- 0.15 * limits
# axis_pos <- -0.6 * limits
# adj <- function(x) axis_pos + x * axis_scale
theta <- seq(0, 2 * pi, length = 50)
circle <- data.frame(c1 = adj(cos(theta)), c2 = adj(sin(theta)))

@@

# axis_scale <- 2 * limits/3
# axis_pos <- -0.4 * limits

axis_scale <- limits/6
axis_pos <- -2/3 * limits

@@

# axis_scale <- 0.1 * limits
# axis_pos <- -0.4 * limits
# adj <- function(x) axis_pos + x * axis_scale
theta <- seq(0, 2 * pi, length = 50)
circle <- data.frame(c1 = adj(cos(theta)), c2 = adj(sin(theta)))

@@

```{r}
#| label: fig-scurve-true-sc
#| fig-cap: "Two views of the true model (blue lines) in $2\\text{-}D$ projections from $7\\text{-}D$, for the S-curve data (black points). The data is spread along the S shape, and does not vary much from this curve. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/I5GL23vLiw0>)." 
#| fig-width: 10
#| fig-height: 6
#| fig-pos: H
